---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ADS8192

<!-- badges: start -->
  [![pkgdown](https://github.com/lmuir16/ADS8192/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/lmuir16/ADS8192/actions/workflows/pkgdown.yaml)
  <!-- badges: end -->

ADS8192 provides a lightweight pipeline for building and analyzing gene
co-expression networks from bulk RNA-seq data. Starting from a
`SummarizedExperiment` object, the package supports the full workflow
from data preparation through network construction, module detection,
visualization, and export.

## Installation

You can install the development version of ADS8192 from
[GitHub](https://github.com/lmuir16/ADS8192) with:

```r
# install.packages("pak")
pak::pak("lmuir16/ADS8192")
```

## Quick Start

```{r example}
library(ADS8192)

# Load example GTEx skeletal muscle data
data(example_se)

# Prepare expression matrix
se_top <- top_variable_features(example_se, n = 500)
mat    <- prepare_expression_matrix(se_top)

# Build network
cor_mat <- pairwise_corr(mat)
adj_mat <- build_adjacency_mat(cor_mat, cor_threshold = 0.7)
net     <- build_network(adj_mat)

# Detect modules and summarize
gene_mods   <- detect_network_modules(net)
net_summary <- summarize_network(net, gene_mods$modules, gene_mods$modularity)

# Identify hub genes
hub_genes <- get_hub_genes(net, modules = gene_mods$modules, n = 20)
head(hub_genes)
```

## Learn More

See `vignette("getting-started", package = "ADS8192")` for a full
walkthrough of the pipeline.
